Master's Project Journal

### 2019-02-04 tex_files/Journal.tex

>>>>

\section*{Ring Osc}
Tried to get this into a PLL and lock to the reference. Struggled for ~6 hours with it and never got close to locking.

\section*{2x2 Network}
Tried this w/ PA PLL,  couldnt get locking, got something that was "close" to locked with huge amounts of jitter. Will attempt to locate the issue tomorrow. Potentially there is an error in the PLL, or a missing error negation.
